---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
First load activity.csv data to the object called "activity" and look at the dimentions of data and see first few lines of data.
```{r}
activity <- read.csv("./activity.csv", header = TRUE, sep=",")
dim(activity)
head(activity)
```


## What is mean total number of steps taken per day?
Calculate the total number of steps each day and store data to the "stepsperday" object.
```{r}
stepsperday <- tapply(activity$steps, activity$date, sum)
```
Draw histgram steps per day.
```{r}
hist(stepsperday)
```

To calculate the mean and median of steps per day.
```{r}
meanwna <- mean(stepsperday, na.rm=TRUE)
medianwna <- median(stepsperday, na.rm=TRUE)
```
Mean is `r meanwna` and median `r medianwna`.

## What is the average daily activity pattern?
Calculate the average steps per interval for all days, and visualize it in line chart.
```{r}
stepsperint <- aggregate(steps ~ interval, data=activity, FUN=mean, na.rm=FALSE)
plot(stepsperint$interval, stepsperint$steps, type="l")
```

```{r}
maxintstep <- max(stepsperint$steps)
maxint <- stepsperint$interval[which.max(stepsperint$steps)]
```
Max steps of Interval is `r maxintstep` and the Interval is `r maxint`.

## Imputing missing values
NAs are only existing in the column of steps, the total number of missing value is as below.
```{r}
colSums(is.na(activity))
```

Create new object called activitynona by copy it from acrivity object and fill the NA value in the steps columns with rest of the average acrity for all data.
```{r}
activitynona <- activity
activitynona[is.na(activitynona)] <- mean(activity$steps, na.rm=TRUE)
colSums(is.na(activitynona))
```

After filling NAs, recreate the histgram of steps per day.
```{r}
stepsperdaynona <- aggregate(steps ~ date, data=activitynona, sum)
hist(stepsperdaynona$steps)
meannona <- mean(stepsperdaynona$steps, na.rm=TRUE)
mediannona <- median(stepsperdaynona$steps, na.rm=TRUE)
```

Even after filling the NAs with average(steps) the mean and median of steps per day will no change a lot.

New mean is `r meannona` and it was `r meanwna`.

New Median is `r mediannona` and it was `r medianwna`.

## Are there differences in activity patterns between weekdays and weekends?
First add new factor valuable on the data set called weekendflag.
```{r}
library(dplyr)
activitynona <- mutate(activitynona, weekendflag = ifelse(weekdays(strptime(activitynona$date, "%Y-%m-%d")) %in% c("日曜日","土曜日"), "Weekend","Weekday"))
stepsweekofday <- aggregate(steps ~ interval + weekendflag, activitynona, mean)
library(lattice)
xyplot(steps ~ interval | weekendflag, stepsweekofday, type='l', layout=c(1,2))
```

